Autonomous Oceanographic Data Collection towards Estimating Excursion Sets of Vector-valued Random Fields

### 2020-06-15 ans_to_reviewers/answers-to-reviewers.tex

\maketitle

We are grateful to the reviewers for their comments and
suggestions. They have all been considered in this revised
version of our manuscript. We have worked a lot on developing both theoretical results, computational resources, and on the presentation in the paper. To help us in these efforts, we included Cedric Traveletti as co-author because he has contributed significantly on the revised version of the paper.

The principal revisions made to the manuscript are as shown in this list, and they are done to address the main comments of Editors and Reviewers:

\begin{itemize}
\item The motivation for excursion sets (ESs), and in particular that of {\bf{multivariate ESs}}, has been strengthened in this revision. Motivating examples are abundant in medicine where doctors do not solely rely on a single symptom but must see several combined effects before making a diagnosis, for example. Our motivation in the current paper is that temperature and salinity are proxies for more complex biological variables in the ocean, and in several cases they must be jointly high or low for phenomena to occur. For instance, salmon lice larvae are known to depend on relatively high temperature and high salinity to survive. Salmon lice are parasites to salmon, and the bivariate ES for temperature and salinity is hence important to understand for sustainable activities in salmon fisheries.

In the revised manuscript these aspects are largely rewritten into the Introduction, and partly also in Section 2 on the expected integrated Bernoulli variance (EIBV), and partly in the Case Study ({\bf{TO DO 6 AGAIN}}). These changes address some key comments from AE and Rev. 1 in particular.

### 2020-06-16 main_new.tex
updates

Data collection to understand natural and artificial phenomena at sea has typically been based on static buoys, floats, or ship-based methods,
with significant logistical limitations that directly impact coverage
and sampling resolution. Modern methods using satellite remote-sensing
provide large-scale coverage but have limited resolution, are limited
to sensing the surface, and are impacted by cloud cover. Numerical
ocean models similarly find it challenging to provide detail at fine
scale \citep{Lermusiaux:2006}, and also come with computation costs that can be practically limiting. 
%limiting computing resources, no time for hard-core ocean model Navier-Stokes, hence GPs and approximations, etc.
%
\begin{figure}[!h] 
  \centering 
  \subfigure[Illustration of an ocean sensing network and the sense-plan-act control methodology.]{\includegraphics[width =
    0.49\textwidth]{Figures/envir2.pdf}\label{fig:envir1}}
  \hfill
  \subfigure[Frontal patterns off of the Nidelva river, Trondheim, Norway.]{\includegraphics[width =
    0.49\textwidth]{Figures/river_proccess.pdf}\label{fig:nidelven}}
  \caption{\ref{fig:envir1} Traditional ocean observation based on 
    ship-based sampling has been augmented by autonomous
    robotic vehicles. % and their interactions.  
    AUV platforms are an integral part of this network being able to
    reason and make decisions for efficient onboard adaptive sampling.
    % using the sense-plan-act control approach to autonomous control. 
    \ref{fig:nidelven} The interaction of river and ocean creates
    processes that are challenging to map, where the combination of
    statistics and robotics can play a vital role in enabling more
    effective oceanographic observation.\kc{The inset ``AUV robot''
      looks very tacky and ad-hoc; might be best to remove it. Change
      ``ships'' to
      ``Ship'', remove the aerial drone, since we didn't use it and
      don't plan to in this work.}}
  \label{fig:envir} \end{figure}
%
\begin{comment} % Somehow redundant with the parag following below
Mobile robotic platforms \citep{Bellingham07} have contributed significantly to environmental monitoring and sampling. In particular, AUVs have advanced the state of in-situ sampling, and made robotics an integral part of ocean observation, filling parts of the undersampling gap \cite{rudnick03,rudnick18} (See Fig. \ref{fig:envir1}).
\end{comment}
%
The advent of robust mobile robotic platforms \citep{Bellingham07} has
resulted in significant contributions to environmental monitoring and
sampling in the ocean. In particular, autonomous underwater vehicles (AUVs) have advanced the state of data collection and consequently have made robotics an integral part of ocean observation; %our 
previous work by some of the authors of the present paper have contributed to this effort \citep{das11b,Das2015,fossuminformation,fossum18b}.

@@

\begin{figure}[!h] 
  \centering 
  \subfigure[Illustration of an ocean sensing network and the sense-plan-act control methodology.]{\includegraphics[width =
    0.49\textwidth]{Figures/envir2.pdf}\label{fig:envir1}}
  \hfill
  \subfigure[Frontal patterns off of the Nidelva river, Trondheim, Norway.]{\includegraphics[width =
    0.49\textwidth]{Figures/river_proccess.pdf}\label{fig:nidelven}}
  \caption{\ref{fig:envir1} Traditional ocean observation based on 
    ship-based sampling has been augmented by autonomous
    robotic vehicles. % and their interactions.  
    AUV platforms are an integral part of this network being able to
    reason and make decisions for efficient onboard adaptive sampling.
    % using the sense-plan-act control approach to autonomous control. 
    \ref{fig:nidelven} The interaction of river and ocean creates
    processes that are challenging to map, where the combination of
    statistics and robotics can play a vital role in enabling more
    effective oceanographic observation.\kc{The inset ``AUV robot''
      looks very tacky and ad-hoc; might be best to remove it. Change
      ``ships'' to
      ``Ship'', remove the aerial drone, since we didn't use it and
      don't plan to in this work.}}
  \label{fig:envir} \end{figure}

>>>>

Data collection to understand natural and artificial phenomena at sea has typically been based on static buoys, floats, or ship-based methods,
with significant logistical limitations that directly impact coverage
and sampling resolution. Modern methods using satellite remote-sensing
provide large-scale coverage but have limited resolution, are limited
to sensing the surface, and are impacted by cloud cover. Numerical
ocean models similarly find it challenging to provide detail at fine
scale \citep{Lermusiaux:2006}, and also come with computation costs that can be practically limiting. 
%limiting computing resources, no time for hard-core ocean model Navier-Stokes, hence GPs and approximations, etc.
%
\begin{figure}[!h] 
  \centering 
  \subfigure[Illustration of an ocean sensing network and the sense-plan-act control methodology.]{\includegraphics[width =
    0.49\textwidth]{Figures/envir.pdf}\label{fig:envir1}}
  \hfill
  \subfigure[Frontal patterns off of the Nidelva river, Trondheim, Norway.]{\includegraphics[width =
    0.49\textwidth]{Figures/river_proccess.pdf}\label{fig:nidelven}}
  \caption{\ref{fig:envir1} Traditional ocean observation based on 
    ship-based sampling has been augmented by autonomous
    robotic vehicles. % and their interactions.  
    AUV platforms are an integral part of this network being able to
    reason and make decisions for efficient onboard adaptive sampling.
    % using the sense-plan-act control approach to autonomous control. 
    \ref{fig:nidelven} The interaction of river and ocean creates
    processes that are challenging to map, where the combination of
    statistics and robotics can play a vital role in enabling more
    effective oceanographic observation.\kc{The inset ``AUV robot''
      looks very tacky and ad-hoc; might be best to remove it. Change
      ``ships'' to
      ``Ship'', remove the aerial drone, since we didn't use it and
      don't plan to in this work.}}
  \label{fig:envir} \end{figure}
%
\begin{comment} % Somehow redundant with the parag following below
Mobile robotic platforms \citep{Bellingham07} have contributed significantly to environmental monitoring and sampling. In particular, AUVs have advanced the state of in-situ sampling, and made robotics an integral part of ocean observation, filling parts of the undersampling gap \cite{rudnick03,rudnick18} (See Fig. \ref{fig:envir1}).
\end{comment}
%
The advent of robust mobile robotic platforms \citep{Bellingham07} has
resulted in significant contributions to environmental monitoring and
sampling in the ocean. In particular, autonomous underwater vehicles (AUVs) have advanced the state of data collection and consequently have made robotics an integral part of ocean observation; %our 
previous work by some of the authors of the present paper have contributed to this effort \citep{das11b,Das2015,fossuminformation,fossum18b}.

@@

\begin{figure}[!h] 
  \centering 
  \subfigure[Illustration of an ocean sensing network and the sense-plan-act control methodology.]{\includegraphics[width =
    0.49\textwidth]{Figures/envir.pdf}\label{fig:envir1}}
  \hfill
  \subfigure[Frontal patterns off of the Nidelva river, Trondheim, Norway.]{\includegraphics[width =
    0.49\textwidth]{Figures/river_proccess.pdf}\label{fig:nidelven}}
  \caption{\ref{fig:envir1} Traditional ocean observation based on 
    ship-based sampling has been augmented by autonomous
    robotic vehicles. % and their interactions.  
    AUV platforms are an integral part of this network being able to
    reason and make decisions for efficient onboard adaptive sampling.
    % using the sense-plan-act control approach to autonomous control. 
    \ref{fig:nidelven} The interaction of river and ocean creates
    processes that are challenging to map, where the combination of
    statistics and robotics can play a vital role in enabling more
    effective oceanographic observation.\kc{The inset ``AUV robot''
      looks very tacky and ad-hoc; might be best to remove it. Change
      ``ships'' to
      ``Ship'', remove the aerial drone, since we didn't use it and
      don't plan to in this work.}}
  \label{fig:envir} \end{figure}
